No sign of recovery

### 2018-05-29 Manuscript.Rmd
Figure with consequences for the analyses of the nitrogen deposition effect using current state data.

library(sp)
library(rgeos)

@@

>>>>

@@

```{r figconsequences, out.width = '50%', fig.asp=0.8, fig.width=4, fig.cap="Effect size of Nitrogen deposition on total species richness estimated from applying the Poisson-GLM with species richness as dependend variable and Nitrogen deposition plus other site covariates as predictors using only the surveys from a five-year interval. Within every five-year interval all plots were sampled once."}
# Effect on N deposition model
makemod <- function(year) {
  mod <- glm(SR ~ Elevation + I(Elevation^2) + Precipitation + NTOT + Inclination, family = poisson,
      data = surv %>% filter(yearP >= year & yearP <= (year + 4)))
  arm::sim(mod, nsim)@coef
}

getestim <- function(x) {
  list(meanN = mean(x[, "NTOT"]),
       lowN = quantile(x[, "NTOT"], probs = 0.05),
       upN = quantile(x[, "NTOT"], probs = 0.95))
}

tt <- map(2003:2013, makemod) %>% map(getestim)
res <- tibble(mean = map_dbl(tt, "meanN"),
              low = map_dbl(tt, "lowN"),
              up = map_dbl(tt, "upN"),
              factor = "NTOT",
              period = 2003:2013)

summary(lm(mean ~ period, data = res))

ggplot(res, aes(x = period, y = mean)) +
  geom_errorbar(aes(ymin = low, ymax = up), width = 0.2, lty = 2, col = "grey65") +
  geom_point() +
  geom_line() +
  geom_smooth(method = lm) +
  geom_abline(intercept = 0, slope = 0, lty = 3) +
  labs(x = "Study period", y = "Effect of Nitrogen deposition")
```

### 2018-05-29 Manuscript.tex
Figure with consequences for the analyses of the nitrogen deposition effect using current state data.

>>>>

\begin{verbatim}
## 
## Call:
## lm(formula = mean ~ period, data = res)
## 
## Residuals:
##        Min         1Q     Median         3Q        Max 
## -0.0233852 -0.0119052  0.0008674  0.0105638  0.0238631 
## 
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)  
## (Intercept)  6.804642   3.297836   2.063   0.0691 .
## period      -0.003415   0.001642  -2.079   0.0674 .
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.01723 on 9 degrees of freedom
## Multiple R-squared:  0.3245, Adjusted R-squared:  0.2494 
## F-statistic: 4.323 on 1 and 9 DF,  p-value: 0.06736
\end{verbatim}

\begin{figure}
\includegraphics[width=0.5\linewidth]{Manuscript_files/figure-latex/figconsequences-1} \caption{Effect size of Nitrogen deposition on total species richness estimated from applying the Poisson-GLM with species richness as dependend variable and Nitrogen deposition plus other site covariates as predictors using only the surveys from a five-year interval. Within every five-year interval all plots were sampled once.}\label{fig:figconsequences}
\end{figure}
